---
title: "Day 1 Interactive Session 2"
author: "Grace Lewin"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

### Logs and exponents in R

Some examples of using `log()` function and `exp()` function in R

(you need to write code in code chunks -- shortcut: command, option, i)

```{r}
# Examples of logarithms

log(4)

# Example of exponents

# e^5
exp(5)

# to test that it is using natural log...
# this is asking "to what power do I have to raise e to get e^1?"
log(exp(1)) 
# and this should equal 1
```

### Creating sequences of values

`seq()` function

```{r}
# A sequence from 1 to 20, by increments of 1
ex1 <- seq(from = 1, to = 20, by = 1)

# Vector from 0 to 40 by increments of 0.2
ex2 <- seq(from = 0, to = 40, by = 0.2 )

# Vector from 1 to 5000 by increments of 10
ex3 <- seq(from = 1, to = 5000, by = 10)

```

### Create a function for logistic growth

Given the carrying capacity, initial population, the growth rate, and time, use the logistic growth model to estimate the population at that time.

```{r}

pop_logistic <- function(capacity, init_pop, rate, time_yr) {
  
  capacity/(1 + ((capacity - init_pop) / init_pop) * exp(-rate * time_yr))
  
  
}

# had to run using run button, instead of just running line by line. just fyi.

pop_logistic(capacity = 2580, init_pop = 230, rate = 0.32, time_yr = 2.4)

```

### Try finding population over a sequence of times

```{r}
# Create a vector of times from 0 to 20 by increments of 0.5

time_vec <- seq(from = 0, to = 15, by = 0.5)

```

Now let's estimate the population over that range of times, given capacity = 2580, initial population = 230, rate = 0.32

```{r}
chipmunk_pop <- pop_logistic(capacity = 2580, init_pop = 230, rate = 0.32, time_yr = time_vec)

```

**Always check what comes out to make sure it makes logical sense!!**

### Create a data frame and plot chipmunk population over time

Going to use ggplot2

ggplot2 wants dataframes!

```{r}

# make a data frame
chipmunk_df <- data.frame(time_vec, chipmunk_pop)
chipmunk_df

```

### Create a bare minimum ggplot graph:

```{r}
ggplot(data = chipmunk_df, aes(x = time_vec, y = chipmunk_pop)) +
  geom_point() + 
  labs(x = "Time (years)", 
       y = "Chipmunk population (individuals)",
       title = "Inyo NF chipmunks",
       subtitle = "Yay chipmunks!")
```
